Proposed Solution

### 2016-11-11 Ennan-Proposal/solutions.tex
autocommit

\begin{figure}[!h]
\begin{small}
\belowdisplayskip=-15pt
\abovedisplayskip=-2pt
\begin{align*}
C ::&\ \text{Correct Learning Set}\\
C =&\ \text{\{Configuration Files in Intermediate Representation\}}\\
LR ::&\ \text{Learned Rules} :: \{\textrm{Rule}\}\\
LR =&\ \{ r\ \mid \forall file \in C,\ holds(r,file) \\
&\qquad \ \exists file \in C,\ nontriviallyHolds(r,file)\} 
\end{align*}
\end{small}
\caption{The definition of which rules should be learned by ConfigC}
\label{fig:configC}
\end{figure}

@@

>>>>

\begin{figure}[!h]
\begin{small}
\belowdisplayskip=-15pt
\abovedisplayskip=-2pt
\begin{align*}
C ::&\ \text{Correct Learning Set}\\
C =&\ \text{\{Configuration Files in Intermediate Representation\}}\\
LR ::&\ \text{Learned Rules} :: \{\textrm{Rule}\}\\
LR =&\ \{ r\ \mid \forall file \in C,\ holds(r,file) \land \\
&\qquad \ \exists file \in C,\ nontriviallyHolds(r,file)\} 
\end{align*}
\end{small}
\caption{The definition of which rules should be learned by ConfigC}
\label{fig:configC}
\end{figure}

@@

\begin{figure}[!h]
%\begin{subfigure}{.3\textwidth}
%\begin{lstlisting}[mathescape=true]
%n = {}
%for (c in $C$):
%  n1 = M(c)
%  n = merge(n, n1)
%\end{lstlisting}
%\end{subfigure}%
\begin{subfigure}{.07\textwidth}
\underline{File 1}
\begin{lstlisting}[mathescape=true]
A
B
C
\end{lstlisting}
\end{subfigure}%
\begin{subfigure}{.07 \textwidth}
\phantom{R}
\begin{lstlisting}[mathescape=true]
AB
AC
BC
\end{lstlisting}
\end{subfigure}%
\begin{subfigure}{.1\textwidth}
\underline{File 2}
\begin{lstlisting}[mathescape=true]
A
C
B
\end{lstlisting}
\end{subfigure}%
\end{figure}
As an example of this process consider the situation where the training set contains two files, and the only rule we consider is ordering.
File 1 contains keywords in the order $[A,B,C]$, and file 2 contains the ordred keywords $[A,C,B]$.
File 1 will produce the set of possible rules $AB, BC, AC$ - and file 2 will produce $AC, CB, BC$.
The only rule that holds for all the files in the training set is then $AC$, so only that rule will be included.
